CommonMind Consortium: DLPFC

### 2020-09-20 combined_analysis/diff.networks.Rmd
Update diff networks

@@

```{r null.results, fig.width=5}
p = df_test$P.Value[df_test$Cohort=="MSSM-Penn-Pitt"]
# print(1 - qvalue(p)$pi0)
hist(p, main="P-values under the null in the discovery cohort", xlab="p-value")

@@

>>>>

# Null permuations
```{r diff.networks.perm}

@@

```{r perm.results, fig.width=5}
p = df_test$P.Value[df_test$Cohort=="MSSM-Penn-Pitt"]
# print(1 - qvalue(p)$pi0)
hist(p, main="P-values under the null in the discovery cohort", xlab="p-value")

@@

# Compute difference networks for 1 random permutation
######################################################
